Pillar 1 - Sequential Pattern Mining

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
comment support
comments

## Support
We calculate the support for all rules manually.
```{r}

@@

The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe

```{r function clean_rules}
clean_rules <- function(rules){

@@

}
```
The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
```{r my_ruleInduction}
my_ruleInduction <- function(rules){

>>>>

## Support
We calculate manually the probabilities of:
a) taking a course
b) failing a course
c) getting a low grade
d) getting a grade equal or lower than x (a certain grade).
```{r}

@@

The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe.
```{r function clean_rules}
clean_rules <- function(rules){

@@

}
```
The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade, with a specified confidence.
```{r my_ruleInduction}
my_ruleInduction <- function(rules){
